COMPASS_analysis

### 2020-05-01 Computational Packages/COMPASS/Compass_analysis.Rmd
first commit

```{r COMPASS fits with Yerkes Donors, cache=TRUE, fig.height=10, fig.width=7}
library(dplyr)
library(COMPASS)
DF<-read.csv("/Applications/Old Computer/Day Lab/Data_Flow/Clean/CD4_count.csv")
compass_data<-DF
compass_data<-rename(compass_data, 
    "IFNg&IL4&IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count",
    "IFNg&IL4&IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.1",
    "IFNg&IL4&!IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.2",
    "IFNg&IL4&!IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.3",
    "IFNg&!IL4&IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.4",
    "IFNg&!IL4&IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.5",
    "IFNg&!IL4&!IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.6",
    "IFNg&!IL4&!IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.7",
    "!IFNg&IL4&IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.8",
    "!IFNg&IL4&IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.9",
    "!IFNg&IL4&!IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.10",
    "!IFNg&IL4&!IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.11",
    "!IFNg&!IL4&IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.12",
    "!IFNg&!IL4&IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.13",
    "!IFNg&!IL4&!IL13&TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.14",
    "!IFNg&!IL4&!IL13&!TNFa" = "Singlets.Lymphocytes.LD..CD3..CD4..G.4.13.T..Count.15")

compass_data$TB<-factor(compass_data$TB, levels= c("N","HC","LTBI","TB"))
compass_data$SM<-factor(compass_data$SM, levels= c("N", "X", "SM"))
compass_data$Stim<-factor(compass_data$Stim, levels=c("UN", "PMA", "WCL", "PEP", "SEA", "SWAP"))
metadata<-dplyr::select(compass_data, c("ID","TB","SM","Stim"))
metadata$group<-paste(metadata$TB,metadata$SM)
counts<- as.matrix(select(compass_data, "IFNg&IL4&IL13&TNFa", 
         "IFNg&IL4&IL13&!TNFa", 
         "IFNg&IL4&!IL13&TNFa",
         "IFNg&IL4&!IL13&!TNFa",
         "IFNg&!IL4&IL13&TNFa",
         "IFNg&!IL4&IL13&!TNFa",
         "IFNg&!IL4&!IL13&TNFa",
         "IFNg&!IL4&!IL13&!TNFa",
         "!IFNg&IL4&IL13&TNFa",
         "!IFNg&IL4&IL13&!TNFa",
         "!IFNg&IL4&!IL13&TNFa",
         "!IFNg&IL4&!IL13&!TNFa",
         "!IFNg&!IL4&IL13&TNFa",
         "!IFNg&!IL4&IL13&!TNFa",
         "!IFNg&!IL4&!IL13&TNFa",
         "!IFNg&!IL4&!IL13&!TNFa"))

>>>>

```{r COMPASS fits with Yerkes Donors, cache=TRUE, fig.height=10, fig.width=7}
library(dplyr)
library(COMPASS)
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean")
DF<-read.csv("ICS_CD4_Counts_clean.csv")
compass_data<-DF
compass_data<-rename(compass_data, 
    "IFNg&IL4&IL13&TNFa" = "G_4_13_T",
    "IFNg&IL4&IL13&!TNFa" = "G_4_13_x",
    "IFNg&IL4&!IL13&TNFa" = "G_4_x_T",
    "IFNg&IL4&!IL13&!TNFa" =  "G_4_x_x" ,
    "IFNg&!IL4&IL13&TNFa" = "G_x_13_T" ,
    "IFNg&!IL4&IL13&!TNFa" = "G_x_13_x" ,
    "IFNg&!IL4&!IL13&TNFa" = "G_x_x_T",
    "IFNg&!IL4&!IL13&!TNFa" = "G_x_x_x",
    "!IFNg&IL4&IL13&TNFa" = "x_4_13_T",
    "!IFNg&IL4&IL13&!TNFa" = "x_4_13_x",
    "!IFNg&IL4&!IL13&TNFa" = "x_4_x_T",
    "!IFNg&IL4&!IL13&!TNFa" = "x_4_x_x",
    "!IFNg&!IL4&IL13&TNFa" = "x_x_13_T",
    "!IFNg&!IL4&IL13&!TNFa" = "x_x_13_x",
    "!IFNg&!IL4&!IL13&TNFa" = "x_x_x_T",
    "!IFNg&!IL4&!IL13&!TNFa" = "x_x_x_x")

compass_data$TB<-factor(compass_data$TB, levels= c("N","HC","LTBI","TB"))
compass_data$SM<-factor(compass_data$SM, levels= c("N", "X", "SM"))
compass_data$Stim<-factor(compass_data$Stim, levels=c("UN", "PMA", "WCL", "PEP", "SEA", "SWAP"))
compass_data$ID<-compass_data$Donor
metadata<-dplyr::select(compass_data, c("ID","TB","SM","Stim"))
metadata$group<-paste(metadata$TB,metadata$SM)
counts<- as.matrix(select(compass_data, "IFNg&IL4&IL13&TNFa", 
         "IFNg&IL4&IL13&!TNFa", 
         "IFNg&IL4&!IL13&TNFa",
         "IFNg&IL4&!IL13&!TNFa",
         "IFNg&!IL4&IL13&TNFa",
         "IFNg&!IL4&IL13&!TNFa",
         "IFNg&!IL4&!IL13&TNFa",
         "IFNg&!IL4&!IL13&!TNFa",
         "!IFNg&IL4&IL13&TNFa",
         "!IFNg&IL4&IL13&!TNFa",
         "!IFNg&IL4&!IL13&TNFa",
         "!IFNg&IL4&!IL13&!TNFa",
         "!IFNg&!IL4&IL13&TNFa",
         "!IFNg&!IL4&IL13&!TNFa",
         "!IFNg&!IL4&!IL13&TNFa",
         "!IFNg&!IL4&!IL13&!TNFa"))
